Opening Restaurants During COVID-19 Can Prove Beneficial for Restaurant Revenue in the GTA

### 2021-02-27 outputs/Paper.Rmd
update

\newpage

>>>>

```{r page1, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
library(here)
knitr::include_graphics(here::here("outputs/image/questionnaire1.png"))
```

```{r page2, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
library(here)
knitr::include_graphics(here::here("outputs/image/questionnaire2.png"))
```

```{r page3, echo=FALSE, fig.cap="Screen capture of the first part of the Survey.", out.width = '70%', fig.align="center"} 
library(here)
knitr::include_graphics(here::here("outputs/image/questionnaire3.png"))
```
\newpage
